### 2019-05-30 article_3.tex
syntax error

\PaperTitle{Web-Dashboard} % Article title

\Authors{Marvin Gaube\textsuperscript{1}, Sidney Kuyateh\textsuperscript{1}, Steffen Walter\textsuperscript{1}} % Authors
\affiliation{\textsuperscript{1}\textit{Studiengang Informationstechnik, Fakultät Technik, Duale Schule Baden-Württemberg, Stuttgart}} % Author affiliation

>>>>

\PaperTitle{Web-Dashboard, Dokumentation/Erfahrungsbericht} % Article title

\Authors{Marvin Gaube\textsuperscript{1}, Sidney Kuyateh\textsuperscript{1}, Steffen Walter\textsuperscript{1}} % Authors
\affiliation{\textsuperscript{1}\textit{Studiengang Informationstechnik, Fakultät Technik, Duale Hochschule Baden-Württemberg, Stuttgart}} % Author affiliation
